Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-19 paper/uist_2016/paper.tex
desirability

@@

\subsection{Desirability and Value}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown. Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

\subsection{Frequent Travellers}
Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}). Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds. But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds. The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.

@@

\subsubsection{Visit Frequency}
We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind. Rewinds containing a location visited most frequently by the participant are kept 8\% of the time. This percentage increases significantly if the Rewind contains the location visited least frequently by the participant. Rewinds that include the least visited location are kept 13\% of the time. This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.

>>>>

\subsection{Desirability}
For Rewinds to be useful, they need to have value to their owners. We measured the value of photos and Rewinds by asking participants if they would want to keep the photo or Rewind after seeing it. Overall, participants wished to keep 11\% of the photos they were shown and 15\% of the Rewinds they were shown. Because these were images from third-party services, they are naturally less likely to be desirable than media captured by the user themselves. In this section we will look at how the value of Rewind's digitally-fabricated memories differs between participants who consider themselves frequent travelers and participants who don't. We will also examine how visit frequency and travel companionship affect the desirability of a Rewind.

\subsubsection{GPS usage}
% no significant effects on photo desirability $\chi^2(1,179) = 0.338$, p = 0.2804(> 0.05)
% significant effects on video/trip desirability $\chi^2(1, 177) = 7.319$, p = 0.0034(< 0.01)
% GPS - 26%, non-GPS - 9%

\subsection{Frequent Travellers}
% no significant effects on photo desirability $\chi^2(1,179) = 0.828$, p = 0.1814(> 0.05)
% significant effects on video/trip desirability $\chi^2(1, 179) = 9.754$, p = 0.0009(< 0.01)
% frequent - 21 %, non-frequent - 2%
Our study found that participants who considered themselves frequent travelers were more likely to keep their photos and Rewinds than participants who did not identify as frequent travelers (Figure~\ref{fig:frequencydesire}). Frequent travelers kept 13\% of the photos they were shown and 21\% of Rewinds. But participants who identified as infrequent travelers kept only 7\% of photos and 2\% of Rewinds. The results show that those who consider themselves frequent travelers tend to place higher value on digital memories than those who do not identify as frequent travelers.

\subsubsection{Travel Companions}
% no significant effects on photo desirability $\chi^2(1,94) = 0.071$, p = 0.3948(> 0.05)
% significant effects on video/trip desirability if alpha = 0.1 - $\chi^2(1, 133) = 2.443$, p = 0.059(< 0.1)
% alone - 13%, not alone - 26%

\subsubsection{Distance}
% no significant effects on photo desirability $\chi^2(1,179) = 8.131$, p = 0.1492(> 0.05)
% significant effects on video/trip desirability if alphe = 0.1 -  $\chi^2(5, 177) = 10.084$, p = 0.0729(< 0.1)
% 0 - 0%, 1 - 0%, 2 - 11%,  3 - 10%, 4 - 20%,  5 - 40%

\subsubsection{Visit Frequency}
% no significant effects on photo desirability $\chi^2(1,128) = 0.32$, p = 0.2858(> 0.05)
% most - 15%, least - 10%
%  no significant effects on video/trip desirability $\chi^2(1, 126) = 0.552$, p = 0.2288(> 0.05)
% most - 11%, least - 18%
We found that the desirability of a Rewind is partly influenced by how much the participant visits the location associated with the Rewind. Rewinds containing a location visited most frequently by the participant are kept 8\% of the time. This percentage increases significantly if the Rewind contains the location visited least frequently by the participant. Rewinds that include the least visited location are kept 13\% of the time. This data suggests that Rewinds are more desirable if they portray a trip that has locations that are not visited often.

@@

@@
